---
output: github_document
---


<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
``` 

# Replication-Material: Material deprivation and the Brexit referendum: a spatial multilevel analysis of the interplay between individual and regional deprivation.

This repository provides all materials for replication of results in

> Haußmann, C. and Rüttenauer T. (2023) “Material deprivation and the Brexit referendum: a spatial multilevel analysis of the interplay between individual and regional deprivation”, *European Sociological Review*, OnlineFirst.

Published manuscript available here:

Preprint available here: [https://doi.org/10.1093/esr/jcad057](https://doi.org/10.1093/esr/jcad057)

Date: 2023-09-25 


## Set up

The code for replication of the results requires the following folders: “01\_Script”, “02\_Data”, “03\_Output”. All Stata and R Scripts are required in folder “01\_Script”, all data will be save in “02\_Data”. Original input data (such as Understanding Society, housing prices and deprivation data) are also required in "02\_Data".) 

To reproduce the results of the paper, the scripts need to be executed in the order provided.

The following packages are necessary for reproduction of main results:

```{r pkgs, eval = FALSE} 
library(DescTools)
library(car)
library(effects)
library(extrafont)
library(ggeffects)
library(gginnards)
library(ggplot2)
library(ggstatsplot)
library(grid)
library(gridExtra)
library(haven)
library(interplot)
library(lfe)
library(lme4)
library(lmtest)
library(maps)
library(mapview)
library(margins)
library(nomisr)
library(plm)
library(plyr)
library(psych)
library(readxl)
library(rgdal)
library(rgeos)
library(rmapshaper)
library(sandwich)
library(seg)
library(sf)
library(spdep)
library(stargazer)
library(stars)
library(texreg)
library(tmap)
library(tmaptools)
library(viridisLite)
```

### Scripts: 

- *01_Long-BHPS-UKHLS_retrival.do*: Prepares the longitudinal file of UKHLS with LSOA identifiers. It requires UKDA-6931-stata and UKDA-7248-stata in the "02\_Data" folder. 

- *02_API_Census*: Uses the nomisr API to download census 2011 statistics. It requires an app key at "Add_your_key_here".

- *03_Prepare-Macro_IMD*: Prepares the index of multiple deprivation data.

- *04_Prepare-Macro_Census*: Prepares the census and house price data.

- *05_Data-preparation*: Prepares the variables and data of the UKHLS as retrieved earlier.

- *06_Descriptives*: Descriptive maps and supplementary stats. 

- *07_Analysis-Micro*: Performs the main analysis and produces the figures of the multilevel analysis.


## Input Data:

The Understanding Society and Harmonised BHPS Special Licence Access data (12th Edition) is not publicly available because of privacy restrictions, but access can be acquired via the UK Data Service (SN: 7248, [https://doi.org/10.5255/UKDA-SN-7248-12](https://doi.org/10.5255/UKDA-SN-7248-12)) after application. The 2015 English Index of Multiple Deprivation in online available at [https://www.gov.uk/government/statistics/english-indices-of-deprivation-2015](https://www.gov.uk/government/statistics/english-indices-of-deprivation-2015), and the 2011 Census data is online available at [https://www.nomisweb.co.uk/sources/census_2011](https://www.nomisweb.co.uk/sources/census_2011). R 4.2.2 was used for data analysis, and code for replication will be made available at [https://github.com/ruettenauer/brexit-deprivation](https://github.com/ruettenauer/brexit-deprivation).

Shapefiles on LSOAs and their centroids can be found online at ONS Open Geography Portal: [https://geoportal.statistics.gov.uk/](https://geoportal.statistics.gov.uk/)

The following data is required in the "02\_Data" folder:

- *UKDA-6931-stata*: Folder containing original Stata data of the BHPS UKHLS data.

- *UKDA-7248-stata*: Folder containing the geo identifiers for the the BHPS UKHLS data.

- *File_7_ID_2015_All_ranks__deciles_and_scores_for_the_Indices_of_Deprivation__and_population_denominators*: English indices of deprivation 2015 from [https://www.gov.uk/government/statistics/english-indices-of-deprivation-2015](https://www.gov.uk/government/statistics/english-indices-of-deprivation-2015).

- *EU_referendum_result_data.csv*: Official results from [https://data.london.gov.uk/dataset/eu-referendum-results](https://data.london.gov.uk/dataset/eu-referendum-results)

- *Lower_Layer_Super_Output_Areas_(December_2011)_Boundaries_Generalised_Clipped_(BGC)_EW_V3-shp*: Shapefiles of the 2011 LSOAs.

- *NUTS_Level_1_(January_2018)_Boundaries*: Shapefiles for NUTS1 regions.

- *hpssadataset46medianpricepaidforresidentialpropertiesbylsoa.xls*: Median House Price data from [https://www.ons.gov.uk/peoplepopulationandcommunity/housing/datasets/medianpricepaidbylowerlayersuperoutputareahpssadataset46](https://www.ons.gov.uk/peoplepopulationandcommunity/housing/datasets/medianpricepaidbylowerlayersuperoutputareahpssadataset46).


## System and version information

Platform: x86_64-w64-mingw32/x64 (64-bit)

Version: R version 4.3.1
